\documentclass[handout,nooutcomes,noauthor]{Ximera}
\input{preamble.tex}
\addtolength{\oddsidemargin}{-.5in}
\addtolength{\evensidemargin}{-.5in}
\addtolength{\textwidth}{1in}

\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1in}
\outcome{Student makes decisions about function properties based on given properties}
\outcome{}

\author{Kevin James}

\title{Limits and Continuity}

\begin{document}
	\begin{abstract}
		This will test students ability to interpret limits.
	\end{abstract}

	\maketitle
	
	\textbf{General Directions:}  Answer each question thoroughly.  Incorrect answers with work shown may receive partial credit, but unsubstantiated answers will receive NO CREDIT.  I do not want (decimal) approximations unless specifically asked for.  I want the exact numbers.  Justify all claims using calculus concepts (i.e., theorems, definitions, etc.).  I am looking for mathematical logic and reasoning.  Show all of your work!! Explain!  Explain!  Explain!  Four points will be dedicated to how you perform as a group.
	\vspace{5mm}
	
	\begin{enumerate}[label=\arabic*.]
		\item Let $ g $ be a function with the following properties.  Determine if each statement below is always true, sometimes true, or never true.  Justify your answers.
		\begin{itemize}
			\item $ \lim\limits_{x \to -\infty}g(x)=-5, \ \lim\limits_{x \to -2}g(x)=4, \ \lim\limits_{x \to 0^-}g(x)=-1, \lim\limits_{x \to 0^+}g(x)=1,  $ and $ \lim\limits_{x \to 3}g(x)=-2 $
			\item $ g(-2)=2, \ g(0)=0, \ g(3)=-2, \ g(5)=7,  $ and $ g(-4) \text{is undefined} $
		\end{itemize}
		\begin{enumerate}[label=(\alph*)]
			\item The graph of $ g $ has a vertical asymptote at $ x=5 $
			\vspace{\stretch{1}}
			\item The graph of $ g $ has a horizontal asymptote.
			\vspace{\stretch{1}}
			\item $ g $ has a removable discontinuity.
			\vspace{\stretch{1}}
			
			\clearpage
		\end{enumerate}
			\textbf{Recall:}  Let $ g $ be a function with the following properties.  Determine if each statement below is always true, sometimes true, or never true.  Justify your answers.
			\begin{itemize}
				\item $ \lim\limits_{x \to -\infty}g(x)=-5, \ \lim\limits_{x \to -2}g(x)=4, \ \lim\limits_{x \to 0^-}g(x)=-1, \lim\limits_{x \to 0^+}g(x)=1,  $ and $ \lim\limits_{x \to 3}g(x)=-2 $
				\item $ g(-2)=2, \ g(0)=0, \ g(3)=-2, \ g(5)=7,  $ and $ g(-4) \text{is undefined} $
			\end{itemize}
			\vspace{5mm}
		\begin{enumerate}[resume,label=(\alph*)]
			\item $ g $ has a non-removable discontinuity.
			\vspace{\stretch{1}}
			\item The graph of  $ g $ has two distinct horizontal asymptotes.
			\vspace{\stretch{1}}
			\item The domain of $ g $ is $ (-\infty, \infty) $.
			\vspace{\stretch{1}}
		\end{enumerate}
	\end{enumerate}	
\end{document}